---
title: "Code - Excluding SEM"
author: "Hannah van Steenis"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#Libraries
```{r}
library(jmv)#EFA
library(car) #For two-way ANOVA
library(corrr) #Correlation matrix
library(dplyr)
library(extrafont)#font in apa plot
library(ggplot2)
library(ggpubr) #qq plots
library(haven) #Reading SPSS file
library(Hmisc) #Correlation matrix
library(ICC) #for the ICC
library(lavaan)
library(lsr) ##for partial eta squared
library(ltm) #Cronbach's alpha
library(naniar) #NA replacement
library(rstatix)#identifying outliers
library(tidyr)
library(tidyverse)
library(psych) # ordinal alpha
library(sjPlot)
library(officer)
library(DT)

```

#Importing data
```{r}
PROactive <- read_sav("FINAL_Reine_gaming_Pseudo_20230227.sav")
DiFa <- read_sav("DiFa.sav")

#Removing all rows with age < 12
PROactive <- PROactive[!(PROactive$Leeftijd_extended < 12),]
DiFa <- DiFa[!(DiFa$AV_Age < 12 | DiFa$AV_Age > 18),]

```

#PROactive
##Data Preperation
###Removing variables
```{r}
PROactive <- PROactive %>% 
  dplyr::select(-contains(c("_8_11",#removing all participants from the 8-11 age group.
                     "_V2_",
                     "_V3",
                     "_V4",
                     "new_mensen_huis",
                     "ander_huis",
                     "mensen_anderhuis",
                     "Steunthuis",
                     "TijdGames",
                     "Slaap",
                     "slaap",
                     "slapen",
                     "opstaan",
                     "_praten_zorgen_",
                     "uitspraken_gezin",
                     "games",
                     "bezigheid",
                     "thuis_steun",
                     "spelletjes",
                     "bezigheid",
                     "_renamed",
                     "_8_12",
                     "kind_pedsql_13_17_",
                     "kind_algemeen_proactive_extended_12_18",
                     "Praten",
                     "AlgVragenlijst_V1_12_18_leeftijd",
                     "kind_algemeen_proactive_12_18_new_woon_ouders_",
                     "AlgVragenlijst_V22",
                     "AlgVragenlijst_V24",
                     "AlgVragenlijst_V25",
                     "AlgVragenlijst_V26",
                     "AlgVragenlijst_V27",
                     "_SES",
                     "Leeftijd_baseline",
                     "Baseline_8_18_InvulDatum")))

#Adding P to every participant ID
PROactive$participant_ID <- sub("^", "P", PROactive$PatientID_Reine)

PROactive <- PROactive %>% 
  relocate(participant_ID, .before = PatientID_Reine)

#Removing all participants who did not fill out QoL.
PROactive <- subset(PROactive, !is.na(p_tot))

```

### Renaming variables
```{r}
PROactive <- PROactive %>% 
  rename("age" = "Leeftijd_extended",
         "gender" = "PatientGeslachtNr",
         "life_satisfaction_rec" = "CijferLeven_12_18_recode",
         "illness_perception" = "Gezondheid_12_18_recode",
         "living_situation" = "AlgVragenlijst_V1_12_18_baseline")

```

###Transforming variables
```{r}
#Gender
PROactive$gender <- as.character(PROactive$gender)
PROactive$gender <- case_when(
  PROactive$gender == "0" ~ "female",
  PROactive$gender == "1" ~ "male"
)

#Problematic social media use
PROactive$PSMU1 <- as.numeric(PROactive$ProblSocMedia1_12_18_recode)
PROactive$PSMU1 <- case_when(
  PROactive$PSMU1 == 1 ~ 0,
  PROactive$PSMU1 == 2 ~ 1
)

PROactive$PSMU2 <- as.numeric(PROactive$ProblSocMedia2_12_18_recode)
PROactive$PSMU2 <- case_when(
  PROactive$PSMU2 == 1 ~ 0,
  PROactive$PSMU2 == 2 ~ 1
)

PROactive$PSMU3 <- as.numeric(PROactive$ProblSocMedia3_12_18_recode)
PROactive$PSMU3 <- case_when(
  PROactive$PSMU3 == 1 ~ 0,
  PROactive$PSMU3 == 2 ~ 1
)

PROactive$PSMU4 <- as.numeric(PROactive$ProblSocMedia4_12_18_recode)
PROactive$PSMU4 <- case_when(
  PROactive$PSMU4 == 1 ~ 0,
  PROactive$PSMU4 == 2 ~ 1
)

PROactive$PSMU5 <- as.numeric(PROactive$ProblSocMedia5_12_18_recode)
PROactive$PSMU5 <- case_when(
  PROactive$PSMU5 == 1 ~ 0,
  PROactive$PSMU5 == 2 ~ 1
)

#Sum of problematic SMU
PROactive$problematic_SMU_short <- PROactive$PSMU1 + PROactive$PSMU2 +  PROactive$PSMU3 + PROactive$PSMU4 + PROactive$PSMU5

#Making school variable
PROactive$education_level_basisschool <- as.numeric(PROactive$Soortonderwijs1_12_18_recode)
PROactive$education_level_MBO <- as.numeric(PROactive$Soortonderwijs2_12_18_recode)
PROactive$education_level_VMBO <- as.numeric(PROactive$Soortonderwijs3_12_18_recode)
PROactive$education_level_HAVO <- as.numeric(PROactive$Soortonderwijs4_12_18_recode)
PROactive$education_level_VWO_gym <- as.numeric(PROactive$Soortonderwijs5_12_18_recode)
PROactive$education_level_speciaal <- as.numeric(PROactive$Soortonderwijs6_12_18_recode)

PROactive <- PROactive %>% 
  mutate_at(c('education_level_basisschool', 'education_level_MBO', 'education_level_VMBO', 'education_level_HAVO', 'education_level_HAVO', 'education_level_VWO_gym', 'education_level_speciaal'), ~ na_if(.,0))

PROactive_edu <- PROactive[, c('PatientID_Reine', 'education_level_basisschool', 'education_level_MBO', 'education_level_VMBO', 'education_level_HAVO', 'education_level_VWO_gym', 'education_level_speciaal')]

PROactive_edu$education_level_basisschool <- as.character(PROactive_edu$education_level_basisschool)
PROactive_edu$education_level_MBO <- as.character(PROactive_edu$education_level_MBO)
PROactive_edu$education_level_VMBO <- as.character(PROactive_edu$education_level_VMBO)
PROactive_edu$education_level_HAVO <- as.character(PROactive_edu$education_level_HAVO)
PROactive_edu$education_level_VWO_gym <- as.character(PROactive_edu$education_level_VWO_gym)
PROactive_edu$education_level_speciaal <- as.character(PROactive_edu$education_level_speciaal)

PROactive_edu$education_level_basisschool <- case_when(PROactive_edu$education_level_basisschool == "1" ~ "basisschool")
PROactive_edu$education_level_MBO <- case_when(PROactive_edu$education_level_MBO == "1" ~ "MBO")
PROactive_edu$education_level_VMBO <- case_when(PROactive_edu$education_level_VMBO == "1" ~ "middelbareschool")
PROactive_edu$education_level_HAVO <- case_when(PROactive_edu$education_level_HAVO == "1" ~ "middelbareschool")
PROactive_edu$education_level_VWO_gym <- case_when(PROactive_edu$education_level_VWO_gym == "1" ~ "middelbareschool")
PROactive_edu$education_level_speciaal <- case_when(PROactive_edu$education_level_speciaal == "1" ~ "speciaal")

PROactive_edu <- PROactive_edu %>% 
  unite(col = 'education_group', c('education_level_basisschool', 'education_level_MBO', 'education_level_VMBO', 'education_level_HAVO', 'education_level_VWO_gym', 'education_level_speciaal'), na.rm = TRUE, remove = TRUE)

PROactive_edu <- replace(PROactive_edu, PROactive_edu=='', NA)

#Merge with PROactive dataframe
PROactive <- full_join(PROactive, PROactive_edu, by = "PatientID_Reine")

#Removing excessive education variables
PROactive <- PROactive %>% 
  dplyr::select(-contains(c("education_level_")))

```

###Computing new ariables
```{r}
#New categorical illness perception variable
PROactive$illness_perception_cat <- as.character(PROactive$illness_perception)
PROactive$illness_perception_cat <- case_when(
  PROactive$illness_perception_cat == "1" ~ "Excellent",
  PROactive$illness_perception_cat == "2" ~ "Good",
  PROactive$illness_perception_cat == "3" ~ "Tolerable",
  PROactive$illness_perception_cat == "4" ~ "Bad"
)

PROactive$illness_perception_cat <- factor(PROactive$illness_perception_cat, levels=c('Bad', 'Tolerable', 'Good', 'Excellent'))

#Mean centered scores
PROactive <- PROactive %>% 
  mutate(PSMU_C1 = PSMU1 - mean(PSMU1),
         PSMU_C2 = PSMU2 - mean(PSMU2),
         PSMU_C3 = PSMU3 - mean(PSMU3),
         PSMU_C4 = PSMU4 - mean(PSMU4),
         PSMU_C5 = PSMU5 - mean(PSMU5),
         IP_C = illness_perception - mean(illness_perception),
         PSMU_C = problematic_SMU_short - mean(problematic_SMU_short))

```

###Cronbach's alpha
```{r}
#Quality of life
##Total
cba.qol <- PROactive[c("P_V01", "P_V02", "P_V03", "P_V04", "P_V05", "P_V06", "P_V07", "P_V09", "P_V10", "P_V11", "P_V12", "P_V13", "P_V14", "P_V15", "P_V16", "P_V17", "P_V18", "P_V19", "P_V20", "P_V21", "P_V23")]
cronbach.alpha(cba.qol, na.rm = TRUE)

##Lich
cba.qol.lich <- PROactive[c("P_V01", "P_V02", "P_V03", "P_V04", "P_V05", "P_V06", "P_V07")]
cronbach.alpha(cba.qol.lich, na.rm = TRUE)

##Sociaal
cba.qol.soci <- PROactive[c("P_V14", "P_V15", "P_V16", "P_V17", "P_V18")]
cronbach.alpha(cba.qol.soci, na.rm = TRUE)

##School
cba.qol.school <- PROactive[c("P_V19", "P_V20", "P_V21", "P_V23")]
cronbach.alpha(cba.qol.school, na.rm = TRUE)

##Emotioneel
cba.qol.emo <- PROactive[c("P_V09", "P_V10", "P_V11", "P_V12", "P_V13")]
cronbach.alpha(cba.qol.emo, na.rm = TRUE)

```

###SEM
####New Dataset
```{r}
#Removing all variables with NA's on quality of life
PROactive_SEM <- subset(PROactive, !is.na(p_tot))

#Making new variable with PSMU >3 = NA
PROactive_SEM <- PROactive_SEM %>% 
  mutate(PSMU_three = problematic_SMU_short) %>% 
  replace_with_na(replace = list(PSMU_three = c(4, 5)))

table(PROactive_SEM$PatientGroep, useNA = "ifany")
prop.table(table(PROactive_SEM$PatientGroep, useNA = "ifany"))

table(PROactive_SEM$problematic_SMU_short)

```

#### Cronbach's alpha
```{r}
#PSMU
cba.psmu.proactive <- PROactive_SEM[c("ProblSocMedia1_12_18_recode", "ProblSocMedia2_12_18_recode", "ProblSocMedia3_12_18_recode", "ProblSocMedia4_12_18_recode", "ProblSocMedia5_12_18_recode")]
cronbach.alpha(cba.psmu.proactive)
```

#### Descriptives
```{r}
nrow(PROactive_SEM)

#Descriptives
table(PROactive_SEM$gender, useNA = "ifany")

summary(PROactive_SEM$age)
mean(PROactive_SEM$age)
sd(PROactive_SEM$age)

table(PROactive_SEM$education_group, useNA = "ifany")

table(PROactive_SEM$living_situation, useNA = "ifany")

#Central tendencies
mean(PROactive_SEM$problematic_SMU_short, na.rm = TRUE)
sd(PROactive_SEM$problematic_SMU_short, na.rm = TRUE)
var(PROactive_SEM$problematic_SMU_short, na.rm = TRUE)

mean(PROactive_SEM$p_tot)
sd(PROactive_SEM$p_tot)

mean(PROactive_SEM$p_lich)
sd(PROactive_SEM$p_lich)

mean(PROactive_SEM$p_soc)
sd(PROactive_SEM$p_soc)

mean(PROactive_SEM$p_school)
sd(PROactive_SEM$p_school)

mean(PROactive_SEM$p_emo)
sd(PROactive_SEM$p_emo)

mean(PROactive_SEM$illness_perception)
sd(PROactive_SEM$illness_perception)

```

####Correlations
```{r}
# Add a new variable 'gender_num' with male = 1 and female = 0
PROactive_SEM <- PROactive_SEM %>%
  mutate(gender_num = ifelse(gender == "male", 1, ifelse(gender == "female", 0, NA)))

# Verify the new variable
head(PROactive_SEM)

cor.SEM <- PROactive_SEM %>% 
  dplyr::select(problematic_SMU_short, p_tot, p_lich, p_soc, p_school, p_emo, life_satisfaction_rec, age, gender_num)

Hmisc::rcorr(as.matrix(cor.SEM))

# Subset the dataset with the specified variables
cors <- c("problematic_SMU_short", "p_tot", "p_lich", "p_soc", "p_school", "p_emo", "illness_perception", "life_satisfaction_rec", "age", "gender_num")
subset_cors <- PROactive_SEM[, cors, drop = FALSE]
data("subset_cors")
head(subset_cors)
tab_corr(subset_cors)
getwd()

tab_corr(subset_cors,
         triangle = "lower",
         digits = 2,
         file = "Table_2.doc")




```

```{r}
# Calculate means
mean_problematic_SMU_short <- mean(PROactive_SEM$problematic_SMU_short, na.rm = TRUE)
mean_p_tot <- mean(PROactive_SEM$p_tot, na.rm = TRUE)
mean_p_lich <- mean(PROactive_SEM$p_lich, na.rm = TRUE)
mean_p_soc <- mean(PROactive_SEM$p_soc, na.rm = TRUE)
mean_p_school <- mean(PROactive_SEM$p_school, na.rm = TRUE)
mean_p_emo <- mean(PROactive_SEM$p_emo, na.rm = TRUE)
mean_life_satisfaction_rec <- mean(PROactive_SEM$life_satisfaction_rec, na.rm = TRUE)
mean_age <- mean(PROactive_SEM$age, na.rm = TRUE)
mean_hp <- mean(PROactive_SEM$illness_perception, na.rm = TRUE)

# Calculate standard deviations
sd_problematic_SMU_short <- sd(PROactive_SEM$problematic_SMU_short, na.rm = TRUE)
sd_p_tot <- sd(PROactive_SEM$p_tot, na.rm = TRUE)
sd_p_lich <- sd(PROactive_SEM$p_lich, na.rm = TRUE)
sd_p_soc <- sd(PROactive_SEM$p_soc, na.rm = TRUE)
sd_p_school <- sd(PROactive_SEM$p_school, na.rm = TRUE)
sd_p_emo <- sd(PROactive_SEM$p_emo, na.rm = TRUE)
sd_life_satisfaction_rec <- sd(PROactive_SEM$life_satisfaction_rec, na.rm = TRUE)
sd_age <- sd(PROactive_SEM$age, na.rm = TRUE)
sd_hp <- sd(PROactive_SEM$illness_perception, na.rm = TRUE)

# Print the results
means_and_sds <- tibble(
  Variable = c("problematic_SMU_short", "p_tot", "p_lich", "p_soc", "p_school", "p_emo", "life_satisfaction_rec", "age", "illness_perception"),
  Mean = c(mean_problematic_SMU_short, mean_p_tot, mean_p_lich, mean_p_soc, mean_p_school, mean_p_emo, mean_life_satisfaction_rec, mean_age, mean_hp),
  SD = c(sd_problematic_SMU_short, sd_p_tot, sd_p_lich, sd_p_soc, sd_p_school, sd_p_emo, sd_life_satisfaction_rec, sd_age, sd_hp)
)

print(means_and_sds)


```


##Descriptive statistics
```{r}
nrow(PROactive)

table(PROactive$gender, useNA = "ifany")
prop.table(table(PROactive$gender, useNA = "ifany"))

summary(PROactive$age)
mean(PROactive$age)
sd(PROactive$age)

table(PROactive$education_group, useNA = "ifany")
prop.table(table(PROactive$education_group, useNA = "ifany"))

table(PROactive$illness_perception_cat, useNA = "ifany")

table(PROactive$problematic_SMU_short_cat, useNA = "ifany")

table(PROactive$PatientGroep, useNA = "ifany")
prop.table(table(PROactive$PatientGroep, useNA = "ifany"))

#PSMU and LS
mean(PROactive$problematic_SMU_short, na.rm = TRUE)
sd(PROactive$problematic_SMU_short, na.rm = TRUE)
var(PROactive$problematic_SMU_short, na.rm = TRUE)

mean(PROactive$life_satisfaction_rec, na.rm = TRUE)
sd(PROactive$life_satisfaction_rec, na.rm = TRUE)

table(PROactive$problematic_SMU_short)

```

###Descriptive statistics SEM
```{r}
nrow(PROactive_SEM)

table(PROactive_SEM$gender, useNA = "ifany")
prop.table(table(PROactive_SEM$gender, useNA = "ifany"))

summary(PROactive_SEM$age)
mean(PROactive_SEM$age)
sd(PROactive_SEM$age)

mean(PROactive_SEM$problematic_SMU_short)
sd(PROactive_SEM$problematic_SMU_short)

table(PROactive_SEM$education_group, useNA = "ifany")
prop.table(table(PROactive_SEM$education_group, useNA = "ifany"))

mean(PROactive_SEM$illness_perception)
sd(PROactive_SEM$illness_perception)

# Means per QoL group
mean(PROactive_SEM$p_tot)
sd(PROactive_SEM$p_tot)

mean(PROactive_SEM$p_emo)
sd(PROactive_SEM$p_emo)

mean(PROactive_SEM$p_school)
sd(PROactive_SEM$p_school)

mean(PROactive_SEM$p_lich)
sd(PROactive_SEM$p_lich)

mean(PROactive_SEM$p_soc)
sd(PROactive_SEM$p_soc)


```

###Descriptives per illness group
```{r}
#Per patient group
PROactive_SEM %>% 
  group_by(PatientGroep) %>% 
  summarise_at(vars(p_tot), list(name = mean, sd))

PROactive_SEM %>% 
  group_by(PatientGroep) %>% 
  summarise_at(vars(p_lich), list(name = mean, sd))

PROactive_SEM %>% 
  group_by(PatientGroep) %>% 
  summarise_at(vars(p_emo), list(name = mean, sd))

PROactive_SEM %>% 
  group_by(PatientGroep) %>% 
  summarise_at(vars(p_soc), list(name = mean, sd))

PROactive_SEM %>% 
  group_by(PatientGroep) %>% 
  summarise_at(vars(p_school), list(name = mean, sd))

PROactive_SEM %>% 
  group_by(PatientGroep) %>% 
  summarise_at(vars(illness_perception), list(name = mean, sd))

PROactive_SEM %>% 
  group_by(PatientGroep) %>% 
  summarise_at(vars(problematic_SMU_short), list(name = mean, sd))

table(PROactive_SEM$PatientGroep)

```

###Descriptives diagnosed vs. undiagnosed
```{r}
PROactive_SEM <- PROactive_SEM %>% 
  mutate(PG = case_when(
    PatientGroep == "Algemene pediatrie WKZ PRO-ACTIVE" ~ "General Pediatrics",
    PatientGroep == "CF WKZ PRO-ACTIVE" ~ "Diagnosed",
    PatientGroep == "Congenitale hartziekten PRO-ACTIVE WKZ" ~ "Diagnosed",
    PatientGroep == "Kindernefrologie WKZ PRO-ACTIVE" ~ "Diagnosed",
    PatientGroep == "(Auto-)immuunziekten WKZ PRO-ACTIVE" ~ "Diagnosed"
  ))

PROactive_SEM <- PROactive_SEM %>% 
  relocate(PG, .after=PatientGroep)

PROactive_SEM %>% 
  group_by(PG) %>% 
  summarise_at(vars(p_tot), list(p_tot = mean, sd))

PROactive_SEM %>% 
  group_by(PG) %>% 
  summarise(p_tot_mean = mean(p_tot), p_tot_sd = sd(p_tot))

PROactive_SEM %>% 
  group_by(PG) %>% 
  summarise_at(vars(p_lich), list(lich = mean, sd))

PROactive_SEM %>% 
  group_by(PG) %>% 
  summarise_at(vars(p_emo), list(emo = mean, sd))

PROactive_SEM %>% 
  group_by(PG) %>% 
  summarise_at(vars(p_soc), list(soc = mean, sd))

PROactive_SEM %>% 
  group_by(PG) %>% 
  summarise_at(vars(p_school), list(school = mean, sd))

PROactive_SEM %>% 
  group_by(PG) %>% 
  summarise_at(vars(illness_perception), list(illnessperception = mean, sd))

PROactive_SEM %>% 
  group_by(PG) %>% 
  summarise_at(vars(problematic_SMU_short), list(psmu = mean, sd))

table(PROactive_SEM$PG)

```

#DiFa
##Renaming variables
```{r}
DiFa <- DiFa %>% 
  rename("age" = "AV_Age",
         "gender" = "AV3",
         "education_group" = "AV4",
         "primaryschool_year" = "AV5",
         "secondaryschool_year" = "AV6",
         "education_level" = "AV7",
         "birth_country" = "AV8",
         "living_situation" = "AV9",
         "siblings" = "AV10",
         "older_brothers" = "AV11_1",
         "younger_brothers" = "AV11_2",
         "older_sisters" = "AV11_3",
         "younger_sisters" = "AV11_4",
         "passive_SMU" = "AV17",
         "passive_SMU_message" = "AV21",
         "active_SMU_message" = "AV22",
         "active_SMU_posting" = "AV18",
         "active_SMU_liking" = "AV19",
         "smartphone_ownership" = "AV20",
         "life_satisfaction" = "AV47",
         "subjective_smartphone_use" = "AV52"
)

```

##Transforming variables
```{r}
#ID
#Adding P to every participant ID
DiFa$participant_ID <- sub("^", "D", DiFa$adolescent_id)

DiFa <- DiFa %>% 
  relocate(participant_ID, .before = AV_StartDate)

#Gender
DiFa$gender <- as.character(DiFa$gender)
DiFa$gender <- case_when(
  DiFa$gender == "1" ~ "male",
  DiFa$gender == "2" ~ "female"
)

#Education group
DiFa$education_group <- as.character(DiFa$education_group)
DiFa$education_group <- case_when(
  DiFa$education_group == "1" ~ "basisschool",
  DiFa$education_group == "2" ~ "middelbareschool",
  DiFa$education_group == "3" ~ "MBO",
  DiFa$education_group == "4" ~ "HBO"
)

#Education year primary school
DiFa$primaryschool_year <- as.character(DiFa$primaryschool_year)
DiFa$primaryschool_year <- case_when(
  DiFa$primaryschool_year == "1" ~ "groep5",
  DiFa$primaryschool_year == "2" ~ "groep6",
  DiFa$primaryschool_year == "3" ~ "groep7",
  DiFa$primaryschool_year == "4" ~ "groep8"
)

#Education year high school
DiFa$secondaryschool_year <- as.character(DiFa$secondaryschool_year)
DiFa$secondaryschool_year <- case_when(
  DiFa$secondaryschool_year == "1" ~ "1eklas",
  DiFa$secondaryschool_year == "2" ~ "2eklas",
  DiFa$secondaryschool_year == "3" ~ "3eklas",
  DiFa$secondaryschool_year == "4" ~ "4eklas",
  DiFa$secondaryschool_year == "5" ~ "5eklas",
  DiFa$secondaryschool_year == "6" ~ "6eklas"
)

#Education level
DiFa$education_level <- as.character(DiFa$education_level)
DiFa$education_level <- case_when(
  DiFa$education_level == "1" ~ "VMBO_b",
  DiFa$education_level == "2" ~ "VMBO_t",
  DiFa$education_level == "3" ~ "VMBO_HAVO",
  DiFa$education_level == "4" ~ "HAVO",
  DiFa$education_level == "5" ~ "HAVO_VWO",
  DiFa$education_level == "6" ~ "VWO_Gymnasium"
)

#Birth country
DiFa$birth_country <- as.character(DiFa$birth_country)
DiFa$birth_country <- case_when(
  DiFa$birth_country == "1" ~ "Nederland",
  DiFa$birth_country == "3" ~ "Other",
  DiFa$birth_country == "6" ~ "Other"
)

#Living situation
DiFa$living_situation <- as.character(DiFa$living_situation)
DiFa$living_situation <- case_when(
  DiFa$living_situation == "1" ~ "Intact",
  DiFa$living_situation == "2" ~ "Equally divided between mother and father",
  DiFa$living_situation == "3" ~ "Mother and her partner",
  DiFa$living_situation == "4" ~ "Father and his partner",
  DiFa$living_situation == "5" ~ "Mother",
  DiFa$living_situation == "6" ~ "Father",
  DiFa$living_situation == "7" ~ "Other"
)

```

##Calculating new variables
```{r}
#Problematic SMU
DiFa$AV16_1 <- as.numeric(DiFa$AV16_1)
DiFa$AV16_1 <- case_when(
  DiFa$AV16_1 == "1" ~ "1",
  DiFa$AV16_1 == "2" ~ "0",
  DiFa$AV16_1 == "0" ~ "0"
)

DiFa$AV16_2 <- as.numeric(DiFa$AV16_2)
DiFa$AV16_2 <- case_when(
  DiFa$AV16_2 == "1" ~ "1",
  DiFa$AV16_2 == "2" ~ "0",
  DiFa$AV16_2 == "0" ~ "0"
)

DiFa$AV16_3 <- as.numeric(DiFa$AV16_3)
DiFa$AV16_3 <- case_when(
  DiFa$AV16_3 == "1" ~ "1",
  DiFa$AV16_3 == "2" ~ "0",
  DiFa$AV16_3 == "0" ~ "0"
)

DiFa$AV16_4 <- as.numeric(DiFa$AV16_4)
DiFa$AV16_4 <- case_when(
  DiFa$AV16_4 == "1" ~ "1",
  DiFa$AV16_4 == "2" ~ "0",
  DiFa$AV16_4 == "0" ~ "0"
)

DiFa$AV16_5 <- as.numeric(DiFa$AV16_5)
DiFa$AV16_5 <- case_when(
  DiFa$AV16_5 == "1" ~ "1",
  DiFa$AV16_5 == "2" ~ "0",
  DiFa$AV16_5 == "0" ~ "0"
)

DiFa$AV16_6 <- as.numeric(DiFa$AV16_6)
DiFa$AV16_6 <- case_when(
  DiFa$AV16_6 == "1" ~ "1",
  DiFa$AV16_6 == "2" ~ "0",
  DiFa$AV16_6 == "0" ~ "0"
)

DiFa$AV16_7 <- as.numeric(DiFa$AV16_7)
DiFa$AV16_7 <- case_when(
  DiFa$AV16_7 == "1" ~ "1",
  DiFa$AV16_7 == "2" ~ "0",
  DiFa$AV16_7 == "0" ~ "0"
)

DiFa$AV16_8 <- as.numeric(DiFa$AV16_8)
DiFa$AV16_8 <- case_when(
  DiFa$AV16_8 == "1" ~ "1",
  DiFa$AV16_8 == "2" ~ "0",
  DiFa$AV16_8 == "0" ~ "0"
)

DiFa$AV16_9 <- as.numeric(DiFa$AV16_9)
DiFa$AV16_9 <- case_when(
  DiFa$AV16_9 == "1" ~ "1",
  DiFa$AV16_9 == "2" ~ "0",
  DiFa$AV16_9 == "0" ~ "0"
)

#AV16's to numeric
DiFa <- DiFa %>% 
  mutate_at(c('AV16_1', 'AV16_2', 'AV16_3', 'AV16_4', 'AV16_5', 'AV16_6', 'AV16_7', 'AV16_8', 'AV16_9'), as.numeric)

#Problematic SMU in one variable
DiFa$problematic_SMU  <- DiFa$AV16_1 + DiFa$AV16_2 + DiFa$AV16_3 + DiFa$AV16_4 + DiFa$AV16_5 + DiFa$AV16_6 + DiFa$AV16_7 + DiFa$AV16_8 + DiFa$AV16_9

DiFa <- DiFa %>% 
  relocate(problematic_SMU, .after = AV16_9)

#Problematic SMU short, including only variables that were also in PROactive
DiFa$problematic_SMU_short <- DiFa$AV16_1 + DiFa$AV16_2 + DiFa$AV16_3 + DiFa$AV16_5 + DiFa$AV16_7

DiFa <- DiFa %>% 
  relocate(problematic_SMU_short, .after = problematic_SMU)

#Recoding life satisfaction
DiFa$life_satisfaction <- as.numeric(DiFa$life_satisfaction)
DiFa$life_satisfaction_rec <- case_when(
  DiFa$life_satisfaction == "1" ~ "10",
  DiFa$life_satisfaction == "2" ~ "9",
  DiFa$life_satisfaction == "3" ~ "8",
  DiFa$life_satisfaction == "4" ~ "7",
  DiFa$life_satisfaction == "5" ~ "6",
  DiFa$life_satisfaction == "6" ~ "5",
  DiFa$life_satisfaction == "7" ~ "4",
  DiFa$life_satisfaction == "8" ~ "3",
  DiFa$life_satisfaction == "9" ~ "2",
  DiFa$life_satisfaction == "10" ~ "1",
  DiFa$life_satisfaction == "11" ~ "0"
)

DiFa$life_satisfaction_rec <- as.numeric(DiFa$life_satisfaction_rec)

```

## Cronbach's alpha
```{r}
cba.psmu.full.difa <- DiFa[c("AV16_1", "AV16_2", "AV16_3", "AV16_4", "AV16_5", "AV16_6", "AV16_7", "AV16_8", "AV16_9")]
cronbach.alpha(cba.psmu.full.difa, na.rm = TRUE)

```

##Descriptive statistics
```{r}
nrow(DiFa)

table(DiFa$gender)
prop.table(table(DiFa$gender, useNA = "ifany"))

table(DiFa$age)

table(DiFa$education_group, useNA = "ifany")
prop.table(table(DiFa$education_group, useNA = "ifany"))

table(DiFa$education_level, useNA = "ifany")
prop.table(table(DiFa$education_level, useNA = "ifany"))

summary(DiFa$age)
mean(DiFa$age)
sd(DiFa$age)

DiFa %>% 
  group_by(age, problematic_SMU) %>% 
  summarise(N = n())

#Missing data per column
colSums(is.na.data.frame(DiFa))

#Mean PSMU_short and LS
mean(DiFa$problematic_SMU_short, na.rm = TRUE)
sd(DiFa$problematic_SMU_short, na.rm = TRUE)
var(DiFa$problematic_SMU_short, na.rm = TRUE)

mean(DiFa$life_satisfaction_rec, na.rm = TRUE)
sd(DiFa$life_satisfaction_rec, na.rm = TRUE)

##Full PSMU scale
mean(DiFa$problematic_SMU, na.rm = TRUE)
sd(DiFa$problematic_SMU, na.rm = TRUE)
var(DiFa$problematic_SMU, na.rm = TRUE)

table(DiFa$problematic_SMU_short)
table(DiFa$problematic_SMU)

```

##Correlation LS and PSMU
```{r}
#Correlation matrix + significances
cor.DiFa <- DiFa %>% 
  dplyr::select(life_satisfaction_rec, problematic_SMU_short) %>% 
  na.omit()

rcorr(as.matrix(cor.DiFa))

cor.test(DiFa$life_satisfaction_rec, DiFa$problematic_SMU, method = "pearson")

```

```{r}
# Calculate means and standard deviations for DiFa dataframe
mean_life_satisfaction_rec <- mean(DiFa$life_satisfaction_rec, na.rm = TRUE)
mean_problematic_SMU_short <- mean(DiFa$problematic_SMU_short, na.rm = TRUE)
mean_age <- mean(DiFa$age, na.rm = TRUE)
mean_gender <- mean(DiFa$gender, na.rm = TRUE)

sd_life_satisfaction_rec <- sd(DiFa$life_satisfaction_rec, na.rm = TRUE)
sd_problematic_SMU_short <- sd(DiFa$problematic_SMU_short, na.rm = TRUE)
sd_gender <- sd(DiFa$age, na.rm = TRUE)
sd_gender <- sd(DiFa$gender, na.rm = TRUE)

# Print the results in a tibble
means_and_sds <- tibble(
  Variable = c("life_satisfaction_rec", "problematic_SMU_short", "age", "AV3"),
  Mean = c(mean_life_satisfaction_rec, mean_problematic_SMU_short, mean_age, mean_gender),
  SD = c(sd_life_satisfaction_rec, sd_problematic_SMU_short, sd_age, sd_gender)
)

print(means_and_sds)



# Select the relevant columns for correlation analysis
cor_DiFa <- DiFa %>%
  dplyr::select(problematic_SMU_short, life_satisfaction_rec, age, gender)

cor_DiFa <- cor_DiFa %>%
  mutate(gender_num = ifelse(gender == "male", 1, ifelse(gender == "female", 0, NA)))

# Convert all columns to numeric, handling lists and factors
cor_DiFa_clean <- cor_DiFa %>%
  mutate(across(everything(), ~ as.numeric(as.character(.)))) %>%
  mutate(across(everything(), ~ ifelse(is.na(.) | is.nan(.) | is.infinite(.), mean(., na.rm = TRUE), .)))

# Compute the correlation matrix
cor_matrix <- cor(cor_DiFa_clean, use = "pairwise.complete.obs")
rcorr_matrix <- Hmisc::rcorr(as.matrix(cor_DiFa_clean))

# Convert the correlation matrix to a data frame
cor_df <- as.data.frame(round(rcorr_matrix$r, 2))
cor_df$Variable <- rownames(cor_df)

# Print the correlation matrix
print(cor_df)





```

```{r}
# Select the relevant variables from DiFa dataframe
cors <- c("problematic_SMU_short", "life_satisfaction_rec", "age", "gender")
subset_cors <- DiFa[, cors, drop = FALSE]

subset_cors <- subset_cors %>%
  na.omit()

subset_cors <- subset_cors %>%
  mutate(gender = ifelse(gender == "male", 1, ifelse(gender == "female", 0, NA)))

# Convert all columns to numeric, handling lists and factors
subset_cors <- subset_cors %>%
  mutate(across(everything(), ~ as.numeric(as.character(.)))) %>%
  mutate(across(everything(), ~ ifelse(is.na(.) | is.nan(.) | is.infinite(.), mean(., na.rm = TRUE), .)))

# Generate correlation matrix
cor_matrix <- cor(subset_cors, use = "pairwise.complete.obs")

# Calculate correlation using Hmisc::rcorr
rcorr_matrix <- Hmisc::rcorr(as.matrix(subset_cors))

# Generate correlation table
tab_corr(subset_cors,
         triangle = "lower",
         digits = 2,
         file = "Correlation_Table_DiFa.doc")

```


##ICC
```{r}
ICCest(fam_id, problematic_SMU, data = DiFa)

ICCest(fam_id, life_satisfaction_rec, data = DiFa)

```

#Merged data
##Merging datasets
```{r}
#In both datasets --> create ill/not ill variable
DiFa <- DiFa %>% 
  add_column(illness_presence = 0)

DiFa$illness_presence <- as.character(DiFa$illness_presence)
DiFa$illness_presence <- case_when(DiFa$illness_presence == "0" ~ "Healthy")

PROactive <- PROactive %>% 
  add_column(illness_presence = 1)

PROactive$illness_presence <- as.character(PROactive$illness_presence)
PROactive$illness_presence <- case_when(PROactive$illness_presence == "1" ~ "Chronically Ill")

##Removing participants who did not fill out QoL.


#Making new columns with DiFa PSMU names matching PROactive
DiFa <- DiFa %>% 
  mutate(
    PSMU1 = AV16_1,
    PSMU2 = AV16_2,
    PSMU3 = AV16_3,
    PSMU4 = AV16_5,
    PSMU5 = AV16_7 
  )

#Making new datasets with only relevant variables
DiFa_sub <- DiFa %>% 
  dplyr::select(participant_ID, illness_presence, age, gender, living_situation, education_group, life_satisfaction_rec, problematic_SMU_short, PSMU1, PSMU2, PSMU3, PSMU4, PSMU5)

PROactive_sub <- PROactive %>% 
  dplyr::select(participant_ID, illness_presence, age, gender, living_situation, education_group, life_satisfaction_rec, problematic_SMU_short, PSMU1, PSMU2, PSMU3, PSMU4, PSMU5)

#Merging the datasets
data <- rbind(DiFa_sub, PROactive_sub)

##Pivot
sum(is.na(data$PSMU_three))
nrow(data)

sum(is.na(PROactive_sub$PSMU_three))
nrow(PROactive_sub)

sum(is.na(PROactive_SEM$PSMU_three))
nrow(PROactive_SEM)

##PSMU groups
data$PSMU_grp <- as.factor(data$problematic_SMU_short)
data$PSMU_grp <- case_when(
  data$PSMU_grp == "0" ~ "No risk",
  data$PSMU_grp == "1" ~ "No risk",
  data$PSMU_grp == "2" ~ "Risk",
  data$PSMU_grp == "3" ~ "Risk",
  data$PSMU_grp == "4" ~ "Risk",
  data$PSMU_grp == "5" ~ "Risk"
)

#Numeric gender variable
data$gender.num <- as.character(data$gender)
data$gender.num <- case_when(
  data$gender.num == "female" ~ "0",
  data$gender.num == "male" ~ "1"
)
data$gender.num <- as.numeric(data$gender.num)



```

##Cronbach's alpha
```{r}
cba.psmu.data <- data[c("PSMU1", "PSMU2", "PSMU3", "PSMU4", "PSMU5")]
cronbach.alpha(cba.psmu.data, na.rm = TRUE)

cba.psmu.DiFa.five <- DiFa[c("PSMU1", "PSMU2", "PSMU3", "PSMU4", "PSMU5")]
cronbach.alpha(cba.psmu.DiFa.five, na.rm = TRUE)

cba.psmu.PROactive.five <- PROactive[c("PSMU1", "PSMU2", "PSMU3", "PSMU4", "PSMU5")]
cronbach.alpha(cba.psmu.PROactive.five, na.rm = TRUE)

#Ordinal alpha both samples
polychoric(cba.psmu.data) 
polychoric.data <- polychoric(cba.psmu.data) 
alpha(polychoric.data$rho)

#Ordinal alpha PROactive
polychoric(cba.psmu.PROactive.five) #This provides the polychoric correlation matrix. 

polychoric.PROactive <- polychoric(cba.psmu.PROactive.five) #This saves the polychoric correlation matrix, and corresponding tau values.

alpha(polychoric.PROactive$rho) #This provides (raw and standardized) alpha, and corresponding item statistics, based on the data set or matrix that is specified in the brackets.  In the output of this calculation, alpha represents ordinal alpha, because it is based on the polychoric correlation matrix.

guttman(polychoric.PROactive$rho) #This provides alternative estimates of reliability for the data matrix that is specified in brackets (i.e., examplename$rho). In the R output, these estimates are labeled as beta, Guttman bounds L1, L2, L3 (alpha), L4 (max), L5, L6 (smc), TenBerge bounds mu0, mu1, mu2, mu3, alpha of the first PC (=principal component), and the “estimated greatest lower bound based upon communalities”. Since the specified data matrix is, in this case, a polychoric correlation matrix, all the reliability estimates represent ordinal versions.

omega(polychoric.PROactive$rho) # This provides the ordinal versions of the reliability coefficients omega (hierarchical, asymptotic, and total, because their calculation is based on the polychoric correlation matrix).


#Ordinal alpha DiFa
polychoric(cba.psmu.DiFa.five) 
polychoric.DiFa <- polychoric(cba.psmu.DiFa.five) 
alpha(polychoric.DiFa$rho) 

```


##Testing assumptions
###Assumptions t-test
```{r}
#Outliers
data %>% 
  group_by(illness_presence) %>% 
  identify_outliers(problematic_SMU_short)

data %>% 
  group_by(illness_presence) %>% 
  identify_outliers(life_satisfaction_rec)

#Normality
ggqqplot(data, "problematic_SMU_short", facet.by = "illness_presence") +
  ggtitle("PSMU")

ggqqplot(data, "life_satisfaction_rec", facet.by = "illness_presence") +
  ggtitle("Life Satisfaction")

#Equality of variances
data %>% 
  levene_test(problematic_SMU_short ~ illness_presence)

data %>% 
  levene_test(life_satisfaction_rec ~ illness_presence)

```

#### Regression - DiFa
```{r}
#DiFa
DiFa.regression <- lm(life_satisfaction_rec ~ problematic_SMU_short, data = DiFa)

par(mfrow = c(2,2))
plot(DiFa.regression)

#PROactive
PROactive.regression <- lm(life_satisfaction_rec ~ problematic_SMU_short, data = PROactive)

par(mfrow = c(2,2))
plot(PROactive.regression)

```

#### Regression - PROactive SEM
```{r}
## First model
SEM.regression <- lm(p_tot ~ PSMU_C + IP_C + PSMU_C*IP_C, data = PROactive_SEM)

par(mfrow = c(2,2))
plot(SEM.regression)

olsrr::ols_vif_tol(SEM.regression)
```

##Analyses
### T-tests
```{r}
#PSMU
t.test(problematic_SMU_short ~ illness_presence, data = data, var.equal = TRUE)
cohens_d(data, problematic_SMU_short ~ illness_presence)

#Life Satisfaction
t.test(life_satisfaction_rec ~ illness_presence, data = data, var.equal = TRUE)
cohens_d(data, life_satisfaction_rec ~ illness_presence)

```

### Moderated regression
```{r}
#Tijdens onze meeting gaf je aan eerst een regressie met alleen IV en DV te doen, daarna een tweede regressie met daarin ook de moderator en interactie toegevoegd. Bij deze: 
library(lm.beta)

#Making dummy variables
data <- data %>% 
  mutate(illness_presence_dummy = case_when(illness_presence == 'Healthy' ~ 1,
                                            illness_presence == 'Chronically Ill' ~ 0))
#1
MR0.INA.1.AG <- lm(life_satisfaction_rec ~ problematic_SMU_short, data)
summary(MR0.INA.1.AG)  # For unstandardized coefficients
confint(MR0.INA.1.AG, level = 0.95)  # Confidence intervals for unstandardized coefficients

# Get standardized coefficients
MR0.INA.1.AG_standardized <- lm.beta(MR0.INA.1.AG)
summary(MR0.INA.1.AG_standardized)

#2
MR1.INA.1.AG <- lm(life_satisfaction_rec ~ problematic_SMU_short + age + gender.num, data)
summary(MR1.INA.1.AG)  # For unstandardized coefficients
confint(MR1.INA.1.AG, level = 0.95)  # Confidence intervals for unstandardized coefficients

# Get standardized coefficients
MR1.INA.1.AG_standardized <- lm.beta(MR1.INA.1.AG)
summary(MR1.INA.1.AG_standardized)


#3
MR2.INA.AG <- lm(life_satisfaction_rec ~ problematic_SMU_short + illness_presence_dummy + problematic_SMU_short*illness_presence_dummy + age + gender.num, data)
summary(MR2.INA.AG)
confint(MR2.INA.AG, level = 0.95)

MR2.INA.AG_standardized <- lm.beta(MR2.INA.AG)
summary(MR2.INA.AG_standardized)
confint(MR2.INA.AG_standardized)

```

###APA figure
```{r}
#Making graph APA
data <- data %>% 
  mutate(psmu_grp_apa = case_when(PSMU_grp == 'No risk' ~ 'Not-At-Risk',
                                  PSMU_grp == 'Risk' ~ 'At-Risk'))

data %>% 
  filter(! participant_ID == 'D16102') %>% 
  ggline(x = "psmu_grp_apa", 
         y = "life_satisfaction_rec", 
         color = "illness_presence", 
         palette = "grey", 
         xlab = "Social Media Use Group", 
         ylab = "Mean Life Satisfaction", 
         add = "mean_se", na.rm = TRUE,
         point.size = 2,
         shape = "illness_presence") +
  theme(axis.text=element_text(size=14, family = "Times New Roman"),
        axis.title=element_text(size=16, family = "Times New Roman"),
        legend.position = c(0.7, 0.8),
        legend.title = element_blank(),
        legend.text = element_text(size=14, family = "Times New Roman"))

```
